\newcommand{\marianResp}{
    From the first Sunday of Advent until Christmas Eve
    \l{
        \v\ Ángelus Dómini nuntiávit Maríæ
        \r\ Et concépit de Spíritu Sancto.
    }
    \e{
        \v\ The Angel of the LORD brought tidings unto Mary
        \r\ And she conceived by the Holy Ghost.
    }
    \l{
        Oremus.
        Grátiam tuam quáesumus, Dómine, méntibus nostris infúnde; ut qui, ángelo nuntiánte, Christi Fílii tui Incarnatiónem cognóvimus, per passiónem ejus et crucem, ad resurrectiónis glóriam perducámur. Per eúmdem Christum Dóminum nostrum.
        \r\ Amen.
    }
    \e{
        Let us pray.
        Pour forth we beseech Thee, O LORD, Thy grace into our hearts, that we to whom the Incarnation of Christ, Thy Son, was made known by the message of an Angel, may, by His Passion and Cross, be brought to the glory of His Resurrection. Through the same Christ, our Lord.
        \r\ Amen.
    }
    From First Vespers of Christmas until the Presentation
    \l{
        \v\ Post Partum Virgo invioláta permansísti.
        \r\ Dei Génitrix, intercéde pro nobis.
    }
    \e{
        \v\ After childbirth, O Virgin, thou didst remain inviolate.
        \r\ Intercede for us, O Mother of God.
    }
    \l{
        Orémus.
        Deus, qui salútis ætérnæ beátæ Maríæ virginitáte fecúnda humáno géneri práemia præstitísti: tríbue, quáesumus, ut ipsam pro nobis intercédere sentiámus, per quam merúimus, Auctórem vitæ suscípere Dóminum nostrum Jesum Christum Fílium tuum.
        \r\ Amen.
    }
    \e{
        Let us pray.
        O God, Who by the fruitful virginity of blessed Mary, hast given to mankind the rewards of eternal salvation: grant, we beseech Thee, that we may experience her intercession for us, through whom we deserved to receive the Author of life, our Lord Jesus Christ, thy Son.
        \r\ Amen.
    }
}